Homework Report

### 2017-01-31 work/work.tex
Adding propositions to homework report

@@

>>>>

\subsection*{Complexity of Vertex Coloring}
\begin{prop}
Vertex coloring is an NP-hard problem.
\end{prop}

Coloring a graph is computationally complex. It is NP-hard to compute the chromatic number of a given graph \cite{garey}. It is NP-complete to decide if a given graph has a \emph{k-coloring} for a given \(k\). This is because it is easy to verify if a coloring of the given graph is a \emph{k-coloring} in polynomial time. This can be done by iterating through the list of edges and checking that each attached vertex has a different color.\newline

@@

\bibitem{garey}
Garey, M. R., Johnson, D. S., \& Stockmeyer, L. [1976], \emph{Some simplified NP-complete graph problems}, Theoretical computer science, 1(3), 237-267.
